x`---
title: "Validation Tests"
author: "Andrew Lin"
date: "2024-05-09"
output: html_document
---

```{r}
library(tidyverse)
library(RPostgres)

dev <- dbConnect(RPostgres::Postgres(),  
               host = 'crain-aspire-1.cdhessuxqdxg.us-east-1.redshift.amazonaws.com',
               port = 5439,
               user = 'aspireuser',
               password = 'Aspirecrainredshift1',
               dbname = 'dev',
               sslmode='require')


cdb_pelcro<-"select * from pelcro_records.cdb"
cdb_p<-dbGetQuery(dev,cdb_pelcro)

cny_test_pelcro<-"select * from pelcro_records.cny_test_db"
cny_test_p<-dbGetQuery(dev,cny_test_pelcro)

adv_data<-dbGetQuery(dev,"select * from dev.pelcro_records.advantage_query")

invoice_table<-dbGetQuery(dev,"select * from prod.pelcro.invoice")

pelcro_table<-dbGetQuery(dev,"select  * from prod.pelcro.subscription
where ispaid is true")
```

Test 1: Unique Ordernumber, Customernumber, and Pelcro Subscription ID

CBD
```{r}
cdb_p%>%
  group_by(shiptocustomernumber,ordernumber,pelcro_subid)%>%
  mutate(n=n())%>%
  filter(n>1)
```
CNY
```{r}
cny_test_p%>%
  group_by(shiptocustomernumber,ordernumber,pelcro_subid)%>%
  mutate(n=n())%>%
  filter(n>1)
```

Test 2: Make sure all contracts > 2022 from Advantage are captured via subscriptionreference-- missing subscription references are tested to see if there respective contracts have been rolled up.

CDB
```{r}
adv_data%>%
  filter(publicationcode=="CD"|publicationcode=="CDW")%>%
  filter(!subscriptionreference%in%cdb_p$adv_subid)%>%
  filter(expirationissuedate>=as.Date("01-01-2022","%m-%d-%Y"))%>%
  select(shiptocustomernumber,ordernumber,subscriptionreference)%>%
  anti_join(cdb_p,by=c("shiptocustomernumber"="original_adv_cust_value","ordernumber"="ordernumber"))
```
CNY
```{r}
adv_data%>%
  filter(publicationcode=="CN"|publicationcode=="CNW"|publicationcode=="CND"|publicationcode=="NHF")%>%
  filter(!subscriptionreference%in%cny_test_p$adv_subid)%>%
  filter(expirationissuedate>=as.Date("01-01-2022","%m-%d-%Y"))%>%
  select(shiptocustomernumber,ordernumber,subscriptionreference)%>%
  anti_join(cny_test_p,by=c("shiptocustomernumber"="original_adv_cust_value","ordernumber"="ordernumber"))
```


Test 3: All Paid Pelcro subscriptions are captured-- those that are not captured, test to see if it stems from a missing advantage subscription value (ie. discrepancy in the Advantage Query). Will reach out to see how to curb these issues.

CDB

```{r}
pelcro_table%>%
  filter(businessunitcode=="CDB")%>%
  filter(!subscriptionid%in%cdb_p$pelcro_subid)%>%
  select(subscriptionid,oldproviderid)%>%
  mutate(oldproviderid=as.numeric(str_replace_all(oldproviderid,"[^0-9]","")))%>%
  left_join(adv_data,by=c("oldproviderid"="subscriptionreference"))%>%
  filter(!is.na(shiptocustomernumber))

missing_paid_pelcro_cdb<-pelcro_table%>%
  filter(businessunitcode=="CDB")%>%
  filter(!subscriptionid%in%cdb_p$pelcro_subid)%>%
  select(subscriptionid,oldproviderid)%>%
  mutate(oldproviderid=as.numeric(str_replace_all(oldproviderid,"[^0-9]","")))

adv_data%>%
  filter(subscriptionreference%in%missing_paid_pelcro_cdb$oldproviderid)
```

CNY:
```{r}
pelcro_table%>%
  filter(businessunitcode=="CNY")%>%
  filter(!subscriptionid%in%cny_test_p$pelcro_subid)%>%
  select(subscriptionid,oldproviderid)%>%
  mutate(oldproviderid=as.numeric(str_replace_all(oldproviderid,"[^0-9]","")))%>%
  left_join(adv_data,by=c("oldproviderid"="subscriptionreference"))%>%
  filter(!is.na(shiptocustomernumber))

missing_paid_pelcro_cny<-pelcro_table%>%
  filter(businessunitcode=="CNY")%>%
  filter(!subscriptionid%in%cny_test_p$pelcro_subid)%>%
  select(subscriptionid,oldproviderid)%>%
  mutate(oldproviderid=as.numeric(str_replace_all(oldproviderid,"[^0-9]","")))

adv_data%>%
  filter(subscriptionreference%in%missing_paid_pelcro_cny$oldproviderid)
```

Test 4: Comparing active and past due subscription counts from Pelcro (BEST Report Counts)

CDB Capture Rate
```{r}
pelcro_table$subscriptionid<-as.numeric(pelcro_table$subscriptionid)

cdb_total_subs<-pelcro_table%>%
  filter(businessunitcode=="CDB"&ispaid==TRUE)%>%
  filter(subscriptionstatus=="active"|subscriptionstatus=="past_due")%>%
  summarise(total_subs=sum(quantity,na.rm=TRUE))

cdb_al_counts<-cdb_p%>%
  left_join(pelcro_table,by=c("pelcro_subid"="subscriptionid"))%>%
  group_by(pelcro_subid)%>%
  filter(subscriptionstatus=="active"|subscriptionstatus=="past_due")%>%
  summarise(quantity=max(quantity))%>%
  ungroup()%>%
  summarise(total_subs=sum(quantity,na.rm=TRUE))

capture_percentage_cdb<-(cdb_al_counts$total_subs/cdb_total_subs$total_subs)*100
difference_in_subs_cdb<-(cdb_total_subs$total_subs-cdb_al_counts$total_subs)

full_str_cdb<-paste("Capture Rate: ",capture_percentage_cdb," Missing Sub Count: ",difference_in_subs_cdb)

print(full_str_cdb)
```


```{r}
pelcro_table$subscriptionid<-as.numeric(pelcro_table$subscriptionid)

cny_total_subs<-pelcro_table%>%
  filter(businessunitcode=="CNY"&ispaid==TRUE)%>%
  filter(subscriptionstatus=="active"|subscriptionstatus=="past_due")%>%
  summarise(total_subs=sum(quantity,na.rm=TRUE))

cny_al_counts<-cny_test_p%>%
  left_join(pelcro_table,by=c("pelcro_subid"="subscriptionid"))%>%
  group_by(pelcro_subid)%>%
  filter(subscriptionstatus=="active"|subscriptionstatus=="past_due")%>%
  summarise(quantity=max(quantity))%>%
  ungroup()%>%
  summarise(total_subs=sum(quantity,na.rm=TRUE))

capture_percentage_cny<-(cny_al_counts$total_subs/cny_total_subs$total_subs)*100
difference_in_subs_cny<-(cny_total_subs$total_subs-cny_al_counts$total_subs)

full_str_cny<-paste("Capture Rate: ",capture_percentage_cny," Missing Sub Count: ",difference_in_subs_cny)

print(full_str_cny)
```

Missing Values List for Further Testing

CDB
```{r}
pelcro_table%>%
  filter(businessunitcode=="CDB"&ispaid==TRUE)%>%
  filter(subscriptionstatus=="active"|subscriptionstatus=="past_due")%>%
  filter(!subscriptionid%in%cdb_p$pelcro_subid)%>%
  select(subscriptionid,oldproviderid,quantity)%>%
  mutate(oldproviderid=as.numeric(str_replace_all(oldproviderid,"[^0-9]","")))%>%
  left_join(adv_data,by=c("oldproviderid"="subscriptionreference"))%>%
  mutate(has_corresponding_adv_row=firstissuesent)%>%
  select(subscriptionid,oldproviderid,quantity,has_corresponding_adv_row)
```

CNY
```{r}
pelcro_table%>%
  filter(businessunitcode=="CNY"&ispaid==TRUE)%>%
  filter(subscriptionstatus=="active"|subscriptionstatus=="past_due")%>%
  filter(!subscriptionid%in%cny_test_p$pelcro_subid)%>%
  select(subscriptionid,oldproviderid,quantity)%>%
  mutate(oldproviderid=as.numeric(str_replace_all(oldproviderid,"[^0-9]","")))%>%
  left_join(adv_data,by=c("oldproviderid"="subscriptionreference"))%>%
  mutate(has_corresponding_adv_row=firstissuesent)%>%
  select(subscriptionid,oldproviderid,quantity,has_corresponding_adv_row)
```








